Extracting data for time slice analyses

### 2017-09-05 analyses/01-extract-data-for-analyses.Rmd
Paths corrected again

## Loading the discrete morphological matrix
matrix <- ReadMorphNexus(paste0("data/matrices/", slug, ".nex"))

## Loading the FADLAD
FADLAD <- read.csv(paste0("data/FADLAD/", slug, ".csv"), row.names = 1, header = TRUE)

## Loading the tree
tree <- read.nexus(paste0("data/trees/", slug, ".tre"))

@@

## Saving the matrix
save(matrix_nodes, file = paste0("data/processed/ancestral_states.", slug ,".Rda"))
```

@@

```{r}
## Loading the matrix
load(paste0("data/processed/ancestral_states.", slug ,".Rda"))

@@

## Saving the matrix
save(matrix_dist, file = paste0("data/processed/distance_matrix.", slug ,".Rda"))
```

@@

```{r}
## Loading the distance matrices
load(paste0("data/processed/distance_matrix.", slug ,".Rda"))

@@

## Loading the data
matrix <- ReadMorphNexus(paste0("data/matrices/", slugs[slug], ".nex"))
FADLAD <- read.csv(paste0("data/FADLAD/", slugs[slug], ".csv"), row.names = 1, header = TRUE)
tree <- read.nexus(paste0("data/trees/", slugs[slug], ".tre"))

@@

## Estimating the ancestral states (with a uncertainty threshold of 0.95)
matrix_nodes <- AncStateEstMatrix(matrix, tree, estimate.allchars = TRUE,
                                  uncertainty.threshold = 0.95)
save(matrix_nodes, file = paste0("data/processed/ancestral_states.", slugs[slug] ,".Rda"))

## Add ancestral states to nodes
load(paste0("data/processed/ancestral_states.", slugs[slug] ,".Rda"))
row.names(matrix_nodes) <- tree$node.label
matrix$matrix <- rbind(matrix$matrix, matrix_nodes)

## Constructing the distance matrix
matrix_dist <- MorphDistMatrixFast(matrix, distance = "Gower")
save(matrix_dist, file = paste0("data/processed/distance_matrix.", slugs[slug] ,".Rda"))

## Ordinating the matrix - no need to run this here, we will do this in the next script
## load(paste0("data/processed/distance_matrix.", slugs[slug] ,".Rda"))
## morphospace <- cmdscale(matrix_dist, k = nrow(matrix_dist) - 2, add = TRUE)$points

>>>>

## Loading the discrete morphological matrix
matrix <- ReadMorphNexus(paste0("../data/matrices/", slug, ".nex"))

## Loading the FADLAD
FADLAD <- read.csv(paste0("../data/FADLAD/", slug, ".csv"), row.names = 1, header = TRUE)

## Loading the tree
tree <- read.nexus(paste0("../data/trees/", slug, ".tre"))

@@

## Saving the matrix
save(matrix_nodes, file = paste0("../data/processed/ancestral_states.", slug ,".Rda"))
```

@@

```{r}
## Loading the matrix
load(paste0("../data/processed/ancestral_states.", slug ,".Rda"))

@@

## Saving the matrix
save(matrix_dist, file = paste0("../data/processed/distance_matrix.", slug ,".Rda"))
```

@@

```{r}
## Loading the distance matrices
load(paste0("../data/processed/distance_matrix.", slug ,".Rda"))

@@

## Loading the data
matrix <- ReadMorphNexus(paste0("../data/matrices/", slugs[slug], ".nex"))
FADLAD <- read.csv(paste0("../data/FADLAD/", slugs[slug], ".csv"), row.names = 1, header = TRUE)
tree <- read.nexus(paste0("../data/trees/", slugs[slug], ".tre"))

@@

## Estimating the ancestral states (with a uncertainty threshold of 0.95)
matrix_nodes <- AncStateEstMatrix(matrix, tree, estimate.allchars = TRUE,
                                  uncertainty.threshold = 0.95)
save(matrix_nodes, file = paste0("../data/processed/ancestral_states.", slugs[slug] ,".Rda"))

## Add ancestral states to nodes
load(paste0("../data/processed/ancestral_states.", slugs[slug] ,".Rda"))
row.names(matrix_nodes) <- tree$node.label
matrix$matrix <- rbind(matrix$matrix, matrix_nodes)

## Constructing the distance matrix
matrix_dist <- MorphDistMatrixFast(matrix, distance = "Gower")
save(matrix_dist, file = paste0("../data/processed/distance_matrix.", slugs[slug] ,".Rda"))

## Ordinating the matrix - no need to run this here, we will do this in the next script
## load(paste0("../data/processed/distance_matrix.", slugs[slug] ,".Rda"))
## morphospace <- cmdscale(matrix_dist, k = nrow(matrix_dist) - 2, add = TRUE)$points
